---
title: "main"
output: html_document
---

```{r setup, include=FALSE}
library(httr)
library(xml2)
library(lubridate)
library(XML)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(gganimate)
```

## Zhihu Hot data collection

The purpose of this document is to present Zhihu-hot, a project dedicated to crawl and analyze Zhihu hot ranking data.

```{r}
add_headers(user_agent="Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/79.0.3945.79 Safari/537.36")
record<-function(){
web<-GET("https://www.zhihu.com",
    add_headers(Cookie=''))

page<-content(web)
write_html(page,file="w.html")
hot<-read_html("w.html")
hotitem<-xml_find_all(hot,".//section")
all_url<-vector()
all_question<-vector()
all_hot<-vector()
for(i in 1:50){
  this<-hotitem[[i]]
  thiss<-xml_child(this,2)
  qnode<-xml_child(thiss,1)
  question<-xml_attr(qnode,"title")
  q_url<-xml_attr(qnode,"href")
  hotnode<-xml_child(thiss,2)
  hotval<-xml_text(hotnode)
  all_url<-append(all_url,q_url)
  all_hot<-append(all_hot,hotval)
  all_question<-append(all_question,question)
}
data.frame(url=all_url,hot=all_hot,question=all_question,time=rep(now(),50),stringsAsFactors = F)}
```

The function defined above will collect the Zhihu hot ranking data to a dataframe.(in order to run the code, please put your Zhihu account's cookie in the add_headers() statement)

```{r eval=F}
all_res<-data.frame(url=c(),hot=c(),question=c(),time=c(),stringsAsFactors = F)
i=0
while(T){
  i=i+1
  all_res<-bind_rows(all_res,record())
  Sys.sleep(60)
  print(i)
}
saveRDS(all_res,"data.txt")
```

This will continuously collect data each minute until you stop it, and all data can be saved in a file.

## Analysis and Visualization

```{r}
all_res<-readRDS("data.txt")
ress<-all_res%>%
  mutate(hot=as.double(str_extract(hot,"\\d+")))
start<-ress$time[[1]]
ress<-ress%>%
  mutate(interv=as.double(as.duration(time-start)))
resss<-ress%>%
    group_by(interv)%>%
    mutate(RNK=rank(hot, ties.method= "first"))%>%
    ungroup()%>%
    filter(RNK>29)%>%
  mutate(time=with_tz(time,"Asia/Shanghai"))
animate(
  resss%>%
  ggplot()+
    geom_col(aes(x=RNK,y=hot,fill=url),show.legend = FALSE,width = 1,na.rm=F)+
    geom_text(aes(x=RNK,y=mean(hot)*0.6,label=question))+
    transition_time(time)+
    coord_flip()+
    scale_y_log10()+
    ease_aes('linear')+
    labs(title="{with_tz(frame_time,\"Asia/Shanghai\")}"),
    nframes=1000,fps=20
)
```

This is an animation of the top ranking questions in the indicated time range(Pay close attention to the 251 question)

```{r}
resss%>%
  filter(RNK>40)%>%
  ggplot()+
  geom_line(aes(interv,hot,color=url),show.legend=F)+
  scale_y_log10()
```

The question corresponding the purple curve is **如何评价华为回应李洪元被羁押 251 天：支持其运用法律武器维权？**


